Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-02-27 manuscript/manuscript.Rmd
More work on manuscript.

        file_name <- file.path(
          manuscript_dir,
          paste0(
            "robustness_comparison_",
            transformation_method, "_",
            estimation_method, "_", "non_robust.RDS"))

@@

            file_name <- file.path(
              manuscript_dir,
              paste0(
                "robustness_comparison_",
                transformation_method, "_",
                estimation_method, "_",
                robustness_source, "_",
                robustness_weighting_function, ".RDS"))

@@

    h <- nloptr::sbplx(
      x0 = x0,
      fn = .optimisation_inner,
      lower = lower,
      upper = upper,
      control=list("xtol_rel"=1e-2),
      x = data,
      fun_args = experiment$fun_args,
      verbose = verbose)

@@

  # Generate table of asymmetric generalised normal distribution parameters.
  n_distributions <- 3

@@

  lapply(experiments, .optimisation_outer, data=x, verbose=TRUE)

@@

>>>>

        file_name <- file.path(
          manuscript_dir,
          "robustness_comparison",
          paste0(
            transformation_method, "_",
            estimation_method, "_",
            "non_robust.RDS"))

@@

            file_name <- file.path(
              manuscript_dir,
              "robustness_comparison",
              paste0(
                transformation_method, "_",
                estimation_method, "_",
                robustness_source, "_",
                robustness_weighting_function, ".RDS"))

@@

    h <- nloptr::sbplx(
      x0 = x0,
      fn = .optimisation_inner,
      lower = lower,
      upper = upper,
      control=list("xtol_rel"=1e-2, "maxeval"=50),
      x = data,
      fun_args = experiment$fun_args,
      verbose = verbose)

@@

  # Generate table of asymmetric generalised normal distribution parameters.
  n_distributions <- 100L

@@

  # lapply(experiments, .optimisation_outer, data=x, verbose=TRUE)

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
# Compute the (marginal) effect of each parameter.

        file_name <- file.path(
          manuscript_dir,
          "robustness_comparison",
          paste0(
            transformation_method, "_",
            estimation_method, "_",
            "non_robust.RDS"))

        # Only yield arguments if the file does not exist.
        yield(list(
          "name" = "non-robust",
          "method" = transformation_method,
          "estimation_method" = estimation_method,
          "file_name" = file_name,
          "fun_args" = fun_args))
      }

      for(robustness_source in c("empirical_probability", "transformed", "residual")){
        for(transformation_method in transformation_methods){
          for(robustness_weighting_function in c("step", "triangle", "cosine")){

            file_name <- file.path(
              manuscript_dir,
              "robustness_comparison",
              paste0(
                transformation_method, "_",
                estimation_method, "_",
                robustness_source, "_",
                robustness_weighting_function, ".RDS"))

            optimisation_settings <- readRDS(file_name)
            weighting_function_parameters <- list("k1"=optimisation_settings$k1)
            if(!is.null(optimisation_settings$k2)){
              weighting_function_parameters <- c(
                weighting_function_parameters,
                list("k2"=optimisation_settings$k2))
            }

            fun_args <- list(
              "method" = transformation_method,
              "estimation_method" = estimation_method,
              "robust" = TRUE,
              "shift" = TRUE,
              "weighting_function" = paste0(robustness_source, "_", robustness_weighting_function),
              "weighting_function_parameters" = weighting_function_parameters)

            # Only yield arguments if the file does not exist.
            yield(list(
              "name" = paste0(robustness_source, "-", robustness_weighting_function),
              "method" = transformation_method,
              "estimation_method" = estimation_method,
              "file_name" = file_name,
              "fun_args" = fun_args))
          }
        }
      }
    }
  }
)

# Helper function for computing transformer parameters under optimisation
# constraints.
.compute_robust_lambda <- function(
    experiment,
    data){

  # Custom parser.
  ..outlier_parser <- function(
    x,
    fun_args){
    # Create transformer.
    transformer <- suppressWarnings(do.call(
      power.transform::find_transformation_parameters,
      args=c(
        list("x" = x$x),
        fun_args)))

    parameter_data <- list(
      "method" = fun_args$method,
      "estimation_method" = fun_args$estimation_method,
      "weight_method" = fun_args$weight_method,
      "lambda" = transformer@lambda,
      "target_lambda" = target_lambda,
      "shift" = transformer@shift)

  parameter_data <- lapply(
    data,
    ..outlier_parser,
    fun_args = experiment$fun_args)

# Generate table of asymmetric generalised normal distribution parameters.
n_distributions <- 100L

experiments <- coro::collect(experiment_args(manuscript_dir = manuscript_dir))

cl <- parallel::makeCluster(18L)

data <- parallel::parLapplyLB(
  cl = cl,
  X = experiments,
  fun = .compute_robust_lambda,
  data = x,
  chunk.size = 1L)
